Adaptive Safe Strong Screening for Efficient Lasso-Type Problems Optimization over the Solution Path

### 2021-01-19 main.tex
Fix merge.

We combine adaptive EDPP and SSR to form Ada-SSR-EDPP as follows. Let $\lambda_k$ denote the point in the path at which the EDPP reference has been most recently updated, and
%$x_j^Tr(\lambda_k)$ computed and
we want the solution at $\lambda_{k+b}$. First, carry out adaptive EDPP screening. Second, apply adaptive SSR screening to the features that have not been discarded by adaptive EDPP and discard any feature that satisfies $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$. Third, conduct a post-convergence check on the features that were discarded by adaptive SSR but not discarded by adaptive EDPP. This procedure is then repeated for $\lambda_{k+b+1}$ (unless an EDPP update is applied).

@@

In this section we will fill in line 11 in Algorithm~\ref{alg:path}. We develop an algorithm to determine when to update the reference for screening. This decision is guided by evaluating screening power at previous $\lambda$ values, and is therefore adaptive, updating the reference more or less frequently as we continue along the solution path. Our goal is to minimize the computation cost, so we will first analyse computation complexity for each part in Algorithm 1. Then we will propose an adaptive algorithm that can minimize the entire computation cost.

\subsubsection{Complexity analysis}

@@

BEDPP is the special case of adaptive EDPP that never updates ($B=K$). When the reference is not updated, safe rule screening will eventually fail to discard any features and the KKT condition checking cost will increase to its maximum, $np$. SEDPP is the special case that updates at every $\lambda$ value ($B=1$). It remains very powerful along the path, making the KKT condition checking cost small, but safe screening updates themselves are costly and require $np$ operations at every $\lambda$-value. Adaptive EDPP can strike a balance between BEDPP and SEDPP. In this example, simply using a fixed batch size $B=10$ can reduce the safe screening cost by 90\% compared to SEDPP and reduce the KKT checking cost by 50\% to more than 90\% compared BEDPP \pb{I find this confusing \ldots by 50\% to more than 90\%?  What does that mean?}.

@@

Safe rules require more significant modification, as EDPP no longer applies. In its place, we use Slores \citep[sparse logistic regression screening rule,][]{wang2014safe}. It was proposed as a one-step rule but can be extended to an adaptive rule with minimal changes. %Let $\Tilde{y}=2y-1\in\{-1,1\}^n$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.

@@

Then $\hat{\beta}_j(\lambda_{k+b})=0$ if
  \begin{equation}
    \max_{\xi=\pm1} T_\xi(\lambda_{k+b},x_j;r(\lambda_k))
  \end{equation}
  \pb{This appears to be missing something. This is not a true/false expression, it's just a number.}
\end{theorem}

>>>>

We combine adaptive EDPP and SSR to form Ada-SSR-EDPP as follows. Let $\lambda_k$ denote the point in the path at which the EDPP reference has been most recently updated, and
we want the solution at $\lambda_{k+b}$. First, carry out adaptive EDPP screening. Second, apply adaptive SSR screening to the features that have not been discarded by adaptive EDPP and discard any feature that satisfies $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$. Third, conduct a post-convergence check on the features that were discarded by adaptive SSR but not discarded by adaptive EDPP. This procedure is then repeated for $\lambda_{k+b+1}$ (unless an EDPP update is applied).

@@

In this section we will fill in line 11 in Algorithm~\ref{alg:path}. We develop an algorithm to determine when to update the reference for screening. This decision is guided by evaluating screening power at previous $\lambda$ values, and is therefore adaptive, updating the reference more or less frequently as we continue along the solution path. Our goal is to minimize the computation cost, so we will first analyse computation complexity for each part in Algorithm~\ref{alg:path}. Then we will propose an adaptive algorithm that can minimize the entire computation cost.

\subsubsection{Complexity analysis}
\label{sec:complexity}

@@

BEDPP is the special case of adaptive EDPP that never updates ($B=K$). When the reference is not updated, safe rule screening will eventually fail to discard any features and the KKT condition checking cost will increase to its maximum, $np$. SEDPP is the special case that updates at every $\lambda$ value ($B=1$). It remains very powerful along the path, making the KKT condition checking cost small, but safe screening updates themselves are costly and require $np$ operations at every $\lambda$-value. Adaptive EDPP can strike a balance between BEDPP and SEDPP. In this example, simply using a fixed batch size $B=10$ can reduce the safe rule updating cost by 90\% compared to SEDPP and reduce the KKT checking cost by about 80\% compared to BEDPP.

@@

Safe rules require more significant modification, as EDPP no longer applies. In its place, we use Slores \citep[sparse logistic regression screening rule,][]{wang2014safe}. It was proposed as a one-step rule but can be extended to an adaptive rule with minimal changes.

@@

Then $\hat{\beta}_j(\lambda_{k+b})=0$ if
  \begin{equation}
    \max_{\xi=\pm1} T_\xi(\lambda_{k+b},x_j;r(\lambda_k))<n\lambda_{k+b}
  \end{equation}
\end{theorem}
